Meta-analysis for the Effect of SSRIs on Anxiety

### 2023-02-23 codebook_dat.Rmd
update 2023-02-23 15:57:35

---
title: "Codebook created on 2023-01-01 at 2023-01-01 17:14:20"
output: github_document
---

@@

## Dataset description
The data contains 20 cases and 24 variables.

>>>>

---
title: "Codebook created on 2023-02-23 at 2023-02-23 15:00:58"
output: github_document
---

@@

## Dataset description
The data contains 465 cases and 22 variables.

### 2023-02-23 manuscript/manuscript.Rmd
update 2023-02-23 15:57:35

```{r setup, include=FALSE}
library("worcs")
library(ggplot2)
library(kableExtra)
library(DT)
library(tidySEM)
library(knitr)
library(metafor)
library(pema)
run_everything = FALSE
sensitivity = FALSE
load_data()
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

@@

#Write forest plot to file
xname <- paste0("Hedges' g (", p, ")")
tmp <- df[order(df$vi, decreasing = TRUE), ]
df_es <- data.frame(
    Study = ordered(tmp$paper, levels = unique(tmp$paper)),
    y = 1:nrow(tmp),
    es = tmp$yi,
    lb = tmp$yi - 1.96*sqrt(tmp$vi),
    ub = tmp$yi + 1.96*sqrt(tmp$vi),
    Sample = p)

>>>>

```{r setup, include=FALSE}
library("worcs")
library(ggplot2)
library(kableExtra)
library(DT)
library(tidySEM)
library(knitr)
library(metafor)
library(pema)
run_everything = TRUE
sensitivity = FALSE
load_data()
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

@@

#Write forest plot to file
xname <- paste0("Hedges' g (", p, ")")
tmp <- df[order(df$vi, decreasing = TRUE), ]
tmp$paperlabel <- paste(tmp$paper, tmp$type.of.ssri.and.dose)
df_es <- data.frame(
    Study = ordered(tmp$paperlabel, levels = unique(tmp$paperlabel)),
    y = 1:nrow(tmp),
    es = tmp$yi,
    lb = tmp$yi - 1.96*sqrt(tmp$vi),
    ub = tmp$yi + 1.96*sqrt(tmp$vi),
    Sample = p)
